Unfortunately we don't have strongly dominated strategies in this game so we have a lot of support to check. Let's begin with pure strategies. We can find 2 Nash equilibria :

- $\mathbf{\{x_1\}}\times\mathbf{\{z_2\}}$. Indeed step 3 is verified :
\begin{align*}
    8 =w_1&\ge u_1(y_1,z_2)=5   \\
    7=w_2&\ge u_2(x_1,y_2)=5 \ \ \mbox{and} \ \ 7=w_2\ge u_2(x_1,x_2)=4 
\end{align*}


- $\mathbf{\{y_1\}}\times\mathbf{\{x_2\}}$. Indeed step 3 is verified :
\begin{align*}
    2 =w_1&\ge u_1(x_1,x_2)=0 \\
    9=w_2&\ge u_2(y_1,y_2)=5  \ \ \mbox{and} \ \  9=w_2\ge u_2(y_1,z_2)=1
\end{align*}

\begin{itemize}
  \item[$\bullet$] Randomized vs pure strategy supports
\end{itemize}

Fortunately we can quickly check these support with the payoff equations (step 2). We can also notice that for example if the support $\mathbf{\{x_1\}}\times\mathbf{\{x_2,y_2\}}$  does not lead to a Nash equilibrium, the support $\mathbf{\{x_1\}}\times\mathbf{\{x_2,y_2,z_2\}}$ does not lead to a Nash equilibrium too. 

- $\mathbf{\{x_1,y1\}}\times\mathbf{\{x_2\}}$, $\mathbf{\{x_1,y1\}}\times\mathbf{\{y_2\}}$ and $\mathbf{\{x_1,y1\}}\times\mathbf{\{z_2\}}$ does not lead to a Nash equilibria, indeed :
\begin{equation*}
    0\ne2 \ \ 5\ne6 \ \ 8\ne5
\end{equation*}

- $\mathbf{\{x_1\}}\times\mathbf{\{x_2,y_2\}}$, $\mathbf{\{x_1\}}\times\mathbf{\{x_2,z_2\}}$ and $\mathbf{\{x_1\}}\times\mathbf{\{y_2,z_2\}}$ does not lead to a Nash equilibria, indeed :
\begin{equation*}
    4\ne6 \ \ 4\ne7 \ \ 6\ne7
\end{equation*}

- $\mathbf{\{y_1\}}\times\mathbf{\{x_2,y_2\}}$, $\mathbf{\{y_1\}}\times\mathbf{\{x_2,z_2\}}$ and $\mathbf{\{y_1\}}\times\mathbf{\{y_2,z_2\}}$ does not lead to a Nash equilibria, indeed :
\begin{equation*}
    9\ne5 \ \ 9\ne1 \ \ 5\ne1
\end{equation*}


And so as explain $\mathbf{\{x_1\}}\times\mathbf{\{x_2,y_2,z_2\}}$ and $\mathbf{\{y_1\}}\times\mathbf{\{x_2,y_2,z_2\}}$ does not lead to a Nash equilibria.


\begin{itemize}
  \item[$\bullet$] Fully randomized strategy : two vs two
\end{itemize}

Here we have 3 support to check, first we have :

-$\mathbf{\{x_1,y_1\}}\times\mathbf{\{x_2,y_2\}}$

 We can begin to compute payoff equation (step 2) for player 1 ($i=1$) :
 \begin{align*}
 \sigma_2(x_2)u_1(x_1,x_2) + \sigma_2(y_2)u_1(x_1,y_2) &= \sigma_2(x_2)u_1(y_1,x_2) + \sigma_2(y_2)u_1(y_1,y_2) \\
 0\sigma_2(x_2)+5\sigma_2(y_2)&= 2\sigma_2(x_2) + 6\sigma_2(y_2) \\
 2\sigma_2(x_2)&=-\sigma_2(y_2)
\end{align*}

We know that  probabilities are  always positive so the equation does not hold here. we can stop


-$\mathbf{\{x_1,y_1\}}\times\mathbf{\{x_2,z_2\}}$

Again we first check the payoff equations (step 2), for the player 1 ($i=1$) we have : 
\begin{align*}
 \sigma_2(x_2)u_1(x_1,x_2) + \sigma_2(z_2)u_1(x_1,z_2) &= \sigma_2(x_2)u_1(y_1,x_2) + \sigma_2(z_2)u_1(y_1,z_2) \\
 0\sigma_2(x_2)+8\sigma_2(z_2)&= 2\sigma_2(x_2) + 5\sigma_2(z_2) \\
 \sigma_2(x_2)&=3\sigma_2(z_2)
\end{align*}

Moreover we know that $\sigma_2(x_2) + \sigma_2(z_2) = 1$ and so we find $\sigma_2(x_2)=\frac{3}{4}$ and $\sigma_2(z_2)=\frac{1}{4}$

Now for the player 2 ($i=2$) we have : 
\begin{align*}
 \sigma_1(x_1)u_2(x_1,x_2) + \sigma_1(y_1)u_2(y_1,x_2) &= \sigma_1(x_1)u_2(x_1,z_2) + \sigma_1(y_1)u_2(y_1,z_2) \\
 4\sigma_1(x_1)+9\sigma_1(y_1)&= 7\sigma_1(x_1) + 1\sigma_1(y_1) \\
 3\sigma_1(x_1)&=8\sigma_1(y_1)
\end{align*}

We also know that $\sigma_1(x_1) + \sigma_1(y_1) = 1$ and so we find $\sigma_1(x_1)=\frac{8}{11}$ and $\sigma_1(y_1)=\frac{3}{11}$

WARNING : Here we have to check the step 3 ! (Is this the best response ?) For the player 2 ($i=2$), $e_2=y_2$ with $w_2=\frac{59}{11}$ we obtain :
\begin{equation*}
    \frac{8}{11}6 + \frac{3}{11}5 \le w_2
\end{equation*}
And so this support does not lead to a Nash equilibrium because $\frac{63}{11}>\frac{59}{11}$

-$\mathbf{\{x_1,y_1\}}\times\mathbf{\{y_2,z_2\}}$

Using payoff equations (step 2), for the player 1 ($i=1$) we have : 
\begin{align*}
 \sigma_2(y_2)u_1(x_1,y_2) + \sigma_2(z_2)u_1(x_1,z_2) &= \sigma_2(y_2)u_1(y_1,y_2) + \sigma_2(z_2)u_1(y_1,z_2) \\
 5\sigma_2(x_2)+8\sigma_2(z_2)&= 6\sigma_2(x_2) + 5\sigma_2(z_2) \\
 \sigma_2(x_2)&=3\sigma_2(z_2)
\end{align*}

Moreover we know that $\sigma_2(y_2) + \sigma_2(z_2) = 1$ and so we find $\sigma_2(y_2)=\frac{3}{4}$ and $\sigma_2(z_2)=\frac{1}{4}$

Now for the player 2 ($i=2$) we have : 
\begin{align*}
 \sigma_1(x_1)u_2(x_1,y_2) + \sigma_1(y_1)u_2(y_1,y_2) &= \sigma_1(x_1)u_2(x_1,z_2) + \sigma_1(y_1)u_2(y_1,z_2) \\
 6\sigma_1(x_1)+5\sigma_1(y_1)&= 7\sigma_1(x_1) + 1\sigma_1(y_1) \\
 \sigma_1(x_1)&=4\sigma_1(y_1)
\end{align*}

We also know that $\sigma_1(x_1) + \sigma_1(y_1) = 1$ and so we find $\sigma_1(x_1)=\frac{4}{5}$ and $\sigma_1(y_1)=\frac{1}{5}$

Again we have to check the best response equation (step 3). for the player 2 ($i=2$) $e_2=x_2$ with $w_2=\frac{29}{5}$ we obtain :
\begin{equation*}
    \frac{4}{5}4 + \frac{1}{5}9 \le w_2
\end{equation*}
And this support lead to a Nash equilibrium because $\frac{29}{5}>\frac{25}{5}$



\begin{itemize}
  \item[$\bullet$] Fully randomized strategy 
\end{itemize}

Finally we have the support $\mathbf{\{x_1,y_1\}}\times\mathbf{\{x_2,y_2,z_2\}}$. It's not useful to recompute everything, we can directly see that this support does not lead to a Nash equilibrium. Indeed the payoff equations (step 2) for the player 2 does not hold because the payoff equations for the support $\mathbf{\{x_1,y_1\}}\times\mathbf{\{x_2,y_2\}}$  does not hold.


To conclude we have 3 Nash equilibrium :
\begin{itemize}
  \item[$\bullet$]  $\sigma_1 = \left(x_1,z_2\right)$ with $w_1= \left(8,7\right)$
  \item[$\bullet$]  $\sigma_2 = \left(y_1,x_2\right)$ with $w_2= \left(2,9\right)$
  \item[$\bullet$]  $\sigma_3 = \left( \frac{4}{5}x_1 + \frac{1}{5}y_1, \frac{3}{4}y_2 + \frac{1}{4}z_2\right)$ with $w_3= \left(\frac{23}{4},\frac{29}{5}\right)$
\end{itemize}
